\textsf{\textbf{Droplet Electro-Bouncing in Low-Gravity}}

### 2018-01-08 doc/manuscript/parameter_estimation.tex
covariance and condition MLE estimates

>>>>

\begin{itemize}
\item We seek to maximize the likelyhood $L = k - \frac{\chi^2}{2}$, which is equivalent to maximizing $\chi^2$.
\item Typically, each iteration evaluates the goal function only once or twice, which is why the Nelder-Mead algorithm is comparatively fast if goal function evaluation is the computational bottleneck (Singer and Mead, 2009).
\end{itemize}
